Normas para a realização do relatório de projecto

### 2015-03-21 state.tex
[ADD] applied template

  HyVAL\cite{hyval} was proposed for modeling composition and interaction of video, this kind of video is also called hypervideo, the structure of HyVAL is derived from traditional video, which divides video into segments, scenes, shots and frames hierarchically. This approach is quite limitative if we want to apply hypervideo concepts to videos that don't follow this structure.

  SMIL was introduced to describe temporal behavior of multimedia, for instance, it could be used to overlay subtitles on films. With SMIL it's possible to synchronize multiple sections of video, either in parallel or in sequence, reproduce a different audio, overlay user interface elements with hyperlinks, amongst multiple other functionalities.

@@

  SVG is a format that implements part of SMIL, it allows dynamic changes to inner content in real time, besides that, it also allows to call javascript functions on events such as animation end, mouse over and mouse click.

@@

  By using solid technologies like Javascript, CSS, SVG and HTML5 in a coordinated way, it's possible to raise communications to a new level. For example, with API's like WebGL, it is now possible to manipulate a three dimensional environment in the context of a hypercall. Another example would be a collaborative spreadsheet using WebRTC. With this, hypercalls are not limited to only video, audio and text.

@@

\bibitem{ipv4} Next Generation Internet: IPv4 Address Exhaustion, Mitigation Strategies and Implications for the U.S. - An IEEE-USA White Paper - 2009
\bibitem{natvoip} How NAT-Compatible Are VoIP Applications? Ying-Dar Lin, Chien-Chao Tseng, Cheng-Yuan Ho, and Yu-Hsien Wu, National Chiao Tung University
\bibitem{embedded} Combinando TV Interativa e Hipervídeo - André Leon S. Gradvohl \& Yuzo Iano, Member, IEEE
\bibitem{hyval} A Structured Document Model for Authoring Video-based Hypermedia
\bibitem{ambulant} Video on the Web: Experiences from SMIL and from the Ambulant Annotator - Dick C.A. Bulterman, A.J. Jansen, and Pablo Cesar
\bibitem{smillingweb} A SMIL player for any web browser - Ombretta Gaggi and Luca Danese

\end{thebibliography}

>>>>

  Hypervideo is a kind of video that contains links to any kind of hypermedia, including itself to another point in time. An example of hypermedia application could be a search engine over hypermedia content, like subtitles, in order to jump to a specific point in time.

  HyperCafe \cite{hypercafe} was an experimental project to expose hypervideo concepts that consisted in switching between conversations inside a cafe.

  Detail-on-demand is a subset o hypervideo that allow us to obtain aditional information about something that apears along the video, like obtaining information about a painting that appears in a particular segment. Hyper-Hitchcock\cite{hitchcock} is an editor and player of detail-on-demand video.

  HyVAL\cite{hyval} was proposed for modeling composition and interaction of video with XML, the structure of HyVAL is derived from traditional video, which divides video into segments, scenes, shots and frames hierarchically. This approach is quite limitative if we want to apply hypervideo concepts to videos that don't follow this structure.

  SMIL was introduced to describe temporal behavior of multimedia, for instance, it could be used to overlay subtitles on films. With SMIL it's possible to synchronize multiple sections of video, either in parallel or in sequence, reproduce a different audio track, overlay user interface elements with hyperlinks, amongst multiple other functionalities.

@@

  SVG is a format that incorporates the animation feature of SMIL. Currently SVG allow us to add movement and animate attributes of elements. When embedded on HTML, it allows dynamic changes to inner content in real time, besides that, it also allows to call javascript functions on events such as animation end, mouse over and mouse click.

@@

  By using techonologies that relies only on web standards (CSS, HTML5, Javascript, SVG), it's possible to raise communications to a new level. For example, with API's like WebGL, it is now possible to manipulate a three dimensional environment in the context of a hypercall. Another example would be a collaborative spreadsheet using WebRTC. With this, hypercalls are not limited to only video, audio and text, but also complex user interfaces.

@@

\bibitem{ipv4} Next Generation Internet: IPv4 Address Exhaustion, Mitigation Strategies and Implications for the U.S. - An IEEE-USA White Paper - 2009
\bibitem{natvoip} How NAT-Compatible Are VoIP Applications? Ying-Dar Lin, Chien-Chao Tseng, Cheng-Yuan Ho, and Yu-Hsien Wu, National Chiao Tung University
\bibitem{embedded} Combinando TV Interativa e Hipervídeo - André Leon S. Gradvohl \& Yuzo Iano, Member, IEEE
\bibitem{hyval} A Structured Document Model for Authoring Video-based Hypermedia
\bibitem{ambulant} Video on the Web: Experiences from SMIL and from the Ambulant Annotator - Dick C.A. Bulterman, A.J. Jansen, and Pablo Cesar
\bibitem{smillingweb} A SMIL player for any web browser - Ombretta Gaggi and Luca Danese
\bibitem{hitchcock} Creating Navigable Multi-Level Video Summaries - Frank Shipman, Andreas Girgensohn, Lynn Wilcox
\bibitem{hypercafe} Authoring and Navigating Video in Space and Time - Nitin Sawhney, David Balcom, Ian Smith
\end{thebibliography}

### 2015-03-21 tese/template_project_latex.tex
[ADD] applied template

\documentclass[11pt,twocolumn]{article}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{color}
\usepackage{makeidx}
\usepackage{blindtext}
\usepackage{float}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[hmargin=3cm,vmargin=3.5cm]{geometry}
\usepackage{indentfirst}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\usepackage{eurosym}
\usepackage{url}

\lstset{frame=tb,
  language=C,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

\usepackage{titlesec}
\titleformat{\section}{\hrule \large\bfseries}{\thesection}{1em}{}

\title{Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC}
\author{
	Henrique Lopes Rocha \\ hdlopesrocha91@gmail.com
}

\date{\today}
\begin{document}

\begingroup
\let\onecolumn\twocolumn

	\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Etiam lobortis facilisis sem. Nullam nec mi et neque pharetra sollicitudin. Praesent imperdiet mi nec ante. Donec ullamcorper, felis non sodales commodo, lectus velit ultrices augue, a dignissim nibh lectus placerat pede.
\end{abstract}

\endgroup

@@

\begin{thebibliography}{9}

\bibitem{ipv4} Next Generation Internet: IPv4 Address Exhaustion, Mitigation Strategies and Implications for the U.S. - An IEEE-USA White Paper - 2009
\bibitem{natvoip} How NAT-Compatible Are VoIP Applications? Ying-Dar Lin, Chien-Chao Tseng, Cheng-Yuan Ho, and Yu-Hsien Wu, National Chiao Tung University
\bibitem{embedded} Combinando TV Interativa e Hipervídeo - André Leon S. Gradvohl \& Yuzo Iano, Member, IEEE
\bibitem{hyval} A Structured Document Model for Authoring Video-based Hypermedia
\bibitem{ambulant} Video on the Web: Experiences from SMIL and from the Ambulant Annotator - Dick C.A. Bulterman, A.J. Jansen, and Pablo Cesar
\bibitem{smillingweb} A SMIL player for any web browser - Ombretta Gaggi and Luca Danese
\bibitem{hitchcock} Creating Navigable Multi-Level Video Summaries - Frank Shipman, Andreas Girgensohn, Lynn Wilcox
\bibitem{hypercafe} Authoring and Navigating Video in Space and Time - Nitin Sawhney, David Balcom, Ian Smith
\end{thebibliography}

>>>>

\documentclass{llncs}
\RequirePackage[english]{babel} % Se fizerem o texto em ingles
%\usepackage[portuguese]{babel}   
\usepackage[latin1]{inputenc}

\usepackage{makeidx}  % allows for indexgeneration
\usepackage{graphicx}  % allows for indexgeneration
\usepackage{subfig}  % allows for indexgeneration
\usepackage{color}  % allows for indexgeneration

\begin{document}
\pagestyle{plain}
\mainmatter              % start of the contributions

\title{Normas para a realização do relatório de projecto}
\author{%
	Henrique Lopes Rocha \\
	email1: henrique.rocha@ist.utl.pt \\
}
\institute{Instituto Superior Técnico}

\maketitle              % typeset the title of the contribution

\begin{abstract}
    In here put your abstract. Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. 
\keywords{keyworkd1, keyworkd2, keyworkd3}
\end{abstract}

@@

\subsection{Context}   % English

\subsection{Problem Statement / Solution Statement} % English
\subsection{Thesis Contributions} % English

\subsection{Article Structure} % English

\section{Arquitectura da solução}

\subsection{Methodology} % Section

\subsection{Planned Schedule} % English
Nesta secção devem apresentar uma calendarização esperadas das vossas actividades.

\section{Conclusions} % English

\subsection{Summary} % English
Neste secção deve-se fazer o resumo do trabalho efectuado, retomando a ideia, as contribuições definidas e a forma como estas se materializaram

\section{Conclusions} % English
Nesta secção devem ser retiradas conclusões do trabalho realizado, em face dos resultados obtidos \cite{exemplo}.

\bibliographystyle{splncs03}
\bibliography{references}
